Climate predictor selection and variable reduction methods influence MaxEnt model performance and predictions of climatic suitability

### 2023-06-02 manuscript/manuscript.qmd
Add Acknowledgements and data availability statement

# Introduction

@@

>>>>

# 1. Introduction

@@

**Next paragraphs**

- Review current methods used to select variables, e.g. R2, VIF, PCA, expert opinion, and most recently, automated selection / model-based selection.

- Aims of this paper are to show how variable selection can influence model outputs and inferences.

# 2. Methods and materials

# 3. Results

# 4. Discussion

# Declaration of Competing Interest

The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

# Data availability

All data and code required to reproduce the analyses are available in a public GitHub repository: https://github.com/guysutton/MS_climate_variable_selection_sdm

# Acknlowedgements

CVS and GFS acknowledge funding from the South African Working for Water (WfW) programme of the Department of Forestry, Fisheries and the Environment: Natural Resource Management Programmes (DFFE: NRMP). Funding was also provided by the South African Research Chairs Initiative of the Department of Science and Technology and the National Research Foundation (NRF) of South Africa. Any opinions, finding, conclusions or recommendations expressed in this material are those of the authors and the NRF does not accept any liability in this regard.

# Supplementary materials

# References
